Towards Comparable Active Learning

### 2023-05-31 doc/al_benchmark_paper.tex
reverted to small classifiers for splice and dna

>>>>

\section{Comparison of Different Classifier Sizes}
We tested two different classifier sizes in Splice and DNA:
\begin{itemize}
	\item Small: [24, 12] (2400 parameters)
	\item Big: [24, 48, 48] (5700 parameters)
\end{itemize}
\begin{figure}
	\centering
	\includegraphics[width=0.49\linewidth]{img/supp_dna_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_dna_big.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_dna_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_dna_big.png}
	\caption{Comparison of small and big classifiers for the DNA dataset}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.49\linewidth]{img/supp_splice_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_splice_big.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_splice_small.png}
	\includegraphics[width=0.49\linewidth]{img/supp_micro_splice_big.png}
	\caption{Comparison of small and big classifiers for the Splice dataset}
\end{figure}
